---
title: "DAZONE Round 1"
author: "Hoang-Chau Luong"
date: "5/31/2022"
output:
  html_document:
    number_sections: yes
    toc: yes
    code_folding: hide
    theme: readable
    highlight: haddock
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(tidymodels)
library(here)
library(dunnr)
extrafont::loadfonts(device = "win", quiet = TRUE)
theme_set(theme_td())
set_geom_fonts()
set_palette()
```


# **Import Data & Cleaning**

## **Formating Column Name**

Because the columns name of data have space, this is not format in R. So we need to rename the column by using two ways:

1. Using function `gsub` to replace the space " " by "_", the difference between `sub` and `gsub` that is `gsub` replace all of space in a name. Not the only first space is replaced. 

```{r message=FALSE, warning=FALSE}
inject.dot <- function(df){
  names(df) <- gsub(" ", "_", names(df));
  df
}

category <- read_csv("data/Category.csv")%>%
  inject.dot()
date <- read_csv("data/Date.csv")%>%
  inject.dot()
defect_type <- read_csv("data/Defect_Type.csv")%>%
  inject.dot()
defect <- read_csv("data/Defect.csv")%>%
  inject.dot()
material <- read_csv("data/Material_Type.csv")%>%
  inject.dot()
metrics <- read_csv("data/Metrics.csv")%>%
  inject.dot()
plant <- read_csv("data/Plant.csv")%>%
  inject.dot()
vendor <- read_csv("data/Vendor.csv")%>%
  inject.dot()
```

2. Using built-in function `make.names` and function `rename_all` in `dplyr` package. The only drawback of this approach is only using "." to replace space " ", but not can use "_".

```{r message=FALSE, warning=FALSE, eval = FALSE}
category <- read_csv("data/Category.csv")%>%
  dplyr::rename_all(funs(make.names(.)))
date <- read_csv("data/Date.csv")%>%
  dplyr::rename_all(funs(make.names(.)))
defect_type <- read_csv("data/Defect_Type.csv")%>%
  dplyr::rename_all(funs(make.names(.)))
defect <- read_csv("data/Defect.csv")%>%
  dplyr::rename_all(funs(make.names(.)))
material <- read_csv("data/Material_Type.csv")%>%
  dplyr::rename_all(funs(make.names(.)))
metrics <- read_csv("data/Metrics.csv")%>%
  dplyr::rename_all(funs(make.names(.)))
plant <- read_csv("data/Plant.csv")%>%
  dplyr::rename_all(funs(make.names(.)))
vendor <- read_csv("data/Vendor.csv")%>%
  dplyr::rename_all(funs(make.names(.)))
```

## **Check Whether Data has Missing Values**

1. The first way to count number of missing values is using `select(everything())` and `summarize_all(funs(sum(is.na(.))))` to create all column to contain result of counting missing values, in `funs()` we add function `sum(is.na(.))` meaning count all rows have missing values.

```{r message=FALSE, warning=FALSE, eval = FALSE}
category %>%
  select(everything()) %>%  # replace to your needs
  summarise_all(funs(sum(is.na(.))))
date %>%
  select(everything()) %>%  # replace to your needs
  summarise_all(funs(sum(is.na(.))))
defect %>%
  select(everything()) %>%  # replace to your needs
  summarise_all(funs(sum(is.na(.))))
defect_type %>%
  select(everything()) %>%  # replace to your needs
  summarise_all(funs(sum(is.na(.))))
material %>%
  select(everything()) %>%  # replace to your needs
  summarise_all(funs(sum(is.na(.))))
metrics %>%
  select(everything()) %>%  # replace to your needs
  summarise_all(funs(sum(is.na(.))))
plant %>%
  select(everything()) %>%  # replace to your needs
  summarise_all(funs(sum(is.na(.))))
vendor %>%
  select(everything()) %>%  # replace to your needs
  summarise_all(funs(sum(is.na(.))))
```


2. **Visualize missing value**

```{r message=FALSE, warning=FALSE, eval = FALSE}
missing.values <- metrics %>%
    gather(key = "key", value = "val") %>%
    mutate(is.missing = is.na(val)) %>%
    group_by(key, is.missing) %>%
    summarise(num.missing = n()) %>%
    filter(is.missing==T) %>%
    select(-is.missing) %>%
    arrange(desc(num.missing)) 

missing.values %>%
  ggplot() +
    geom_bar(aes(x=key, y=num.missing), stat = 'identity') +
    labs(x='variable', y="number of missing values", title='Number of missing values') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

missing.values <- metrics %>%
  gather(key = "key", value = "val") %>%
  mutate(isna = is.na(val)) %>%
  group_by(key) %>%
  mutate(total = n()) %>%
  group_by(key, total, isna) %>%
  summarise(num.isna = n()) %>%
  mutate(pct = num.isna / total * 100)

levels <-
    (missing.values  %>% filter(isna == T) %>% arrange(desc(pct)))$key

percentage.plot <- missing.values %>%
      ggplot() +
        geom_bar(aes(x = reorder(key, desc(pct)), 
                     y = pct, fill=isna), 
                 stat = 'identity', alpha=0.8) +
      scale_x_discrete(limits = levels) +
      scale_fill_manual(name = "", 
                        values = c('steelblue', 'tomato3'), labels = c("Present", "Missing")) +
      coord_flip() +
      labs(title = "Percentage of missing values", x =
             'Variable', y = "% of missing values")

percentage.plot

row.plot <- df %>%
  mutate(id = row_number()) %>%
  gather(-id, key = "key", value = "val") %>%
  mutate(isna = is.na(val)) %>%
  ggplot(aes(key, id, fill = isna)) +
    geom_raster(alpha=0.8) +
    scale_fill_manual(name = "",
        values = c('steelblue', 'tomato3'),
        labels = c("Present", "Missing")) +
    scale_x_discrete(limits = levels) +
    labs(x = "Variable",
           y = "Row Number", title = "Missing values in rows") +
    coord_flip()

row.plot

grid.arrange(percentage.plot, row.plot, ncol = 2)
```


After doing exploration, our data do not have any missing values. Congratulation.

# **EDA**

1. **Find which vendor has the most defect product in 2 years 2013 and 2014?**

```{r message=FALSE, warning=FALSE}
metrics %>%
  group_by(Vendor_ID) %>%
  summarise(total_defect_qty = sum(Defect_Qty)) %>%
  arrange(desc(total_defect_qty)) %>%
  right_join(vendor) %>%
  head(10) %>%
  gt::gt()
```

2. **Find which vendor has the most defect product in year 2013 & year 2014**

First, we need to extract year from date to be able to group by.

* We see that format of date in data is `%m/%d/%Y %H:%M`, so we use function format to extract date follow this format of date `format(as.Date(metrics$Date, format="%m/%d/%Y %H:%M"),"%Y")`. After that we gain a year with redundant 2 first 00 number, so then we use function `substr` to extract character from index 3 to 4.

```{r message=FALSE, warning=FALSE}
# gsub(".*/","",metrics$Date)
# substr(metrics$Date, 7, 8)
# 
# format(as.Date(metrics$Date, format="%m/%d/%Y %H:%M"),"%Y")

metrics %>%
  mutate(year = substr(
    format(as.Date(metrics$Date, format="%m/%d/%Y %H:%M"),"%Y"), 3, 4
  )) %>%
  group_by(Vendor_ID, year) %>%
  summarise(total_defect_qty = sum(Defect_Qty)) %>%
  arrange(desc(total_defect_qty)) %>%
  right_join(vendor, by = "Vendor_ID") %>%
  head(10) 
```

   From table we see that:
* `Plustax` has highest defect product in year 2013 with 3486268 defect products
* `Quotelane` has highest  defect product in year 2014 with 2155354 defect products

3. **Company has a highest down time**

```{r message=FALSE, warning=FALSE}
metrics %>%
  group_by(Plant_ID) %>%
  summarize(total_downtime = sum(`Downtime_(min)`)) %>%
  ungroup() %>%
  mutate(percent_downtime = total_downtime/sum(total_downtime)) %>%
  arrange(desc(total_downtime)) %>%
  right_join(plant, by = "Plant_ID") %>%
  head(10) %>%
  gt::gt()
```

* Springfield, IL has highest `total_downtime` with 17311 mins and gain $12.4\%$.

4. **Company has highest defect product**

```{r message=FALSE, warning=FALSE}
metrics %>%
  group_by(Plant_ID) %>%
  summarize(total_defect_qty = sum(Defect_Qty)) %>%
  arrange(desc(total_defect_qty)) %>%
  right_join(plant, by = "Plant_ID") %>%
  head(10) %>%
  gt::gt()
```

From the table we see that:

* Detriot, Ml has a highest defect product with value 6686876.

5. **Which material is better than others materials**

```{r message=FALSE, warning=FALSE}
metrics %>%
  group_by(Material_Type_ID) %>%
  summarize(total_defect_qty = sum(Defect_Qty)) %>%
  arrange(total_defect_qty) %>%
  right_join(material, by = "Material_Type_ID") %>%
  head(10) %>%
  gt::gt()
```

From the table, we see that `Wires` has lowest defect product, so that means this material is better than the others
