---
title: "Round 2: DAZONE"
author: "Hoang-Chau Luong"
date: "06/10/2022"
output:
  html_document:
    number_sections: yes
    toc: yes
    code_folding: hide
    theme: readable
    highlight: haddock
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r warning=FALSE, message=FALSE}
library(tidyverse)
library(lubridate)
options(scipen = 20)

theme_set(theme_light())
```

# **Import data**

## **Front end & Back end**

```{r warning=FALSE, message=FALSE}
front_end <- read_csv("data_round_2/Front-end dataset.csv") %>%
  mutate(date = as.POSIXct(timestamp/1e3, origin = "1970-01-01", tz = "UTC-7")) %>%
  select(-6, -7)

back_end <- read_csv("data_round_2/Back-end dataset.csv") %>%
  mutate(date = as.POSIXct(timestamp/1e3, origin = "1970-01-01", tz = "UTC-7"))

back_end %>%
  inner_join(user_type) %>%
  select(id) %>%
  unique()
  
```

## **New user**

```{r}
new_user <- front_end %>%
  select(id, screenid) %>%
  unique() %>%
  filter(screenid != 11) %>%
  group_by(id) %>%
  summarise(type = "new") %>%
  ungroup()
```

### **Front end new user**

```{r}
front_end_ui <- front_end %>%
  left_join(new_user, by = "id") %>%
  mutate(type = ifelse(is.na(type), "old", type))
```

### **User type**

```{r}
user_type <- front_end_ui %>%
  group_by(id, type) %>%
  summarize(n = n()) %>%
  select(-n) %>%
  ungroup()
```

## **User have B**

```{r}
user_B <- back_end %>%
  filter(stepresult == "B") %>%
  select(id, stepresult) %>%
  unique()
```

## **Back end list id**

```{r}
back_end_list_id <- back_end %>%
  select(id) %>%
  unique()
```

### **Number of B each user**

```{r}
B_status_backend <- back_end %>%
  filter(stepresult == "B") %>%
  group_by(id) %>%
  summarize(B_num = n()) %>%
  right_join(back_end_list_id, by = "id") %>%
  mutate(B_num = ifelse(is.na(B_num), 0, B_num))
```

## **User retry**

```{r}
user_retry <- back_end %>%
  mutate(encode = ifelse(stepresult == "B", 1, 0)) %>%
  group_by(id) %>%
  mutate(next_code = lead(encode, order_by = id)) %>%
  mutate(have_retrived = ((encode == 0 & next_code == 1) | 
                            (encode == 0 & next_code == 0))) %>%
  filter(have_retrived == TRUE) %>%
  select(id) %>%
  unique()
```

### **Number of retry each user**

```{r}
number_user_retry <- back_end %>%
  mutate(encode = ifelse(stepresult == "B", 1, 0)) %>% 
  group_by(id) %>%
  arrange(date) %>% 
  mutate(next_code = lead(encode, order_by = id)) %>% 
  ungroup() %>%
  filter(!is.na(next_code)) %>%
  group_by(id) %>%
  summarize(retry_rate = sum(encode == 0 & next_code == 0) + sum(encode == 0 & next_code == 1)) %>%
  right_join(back_end_list_id) %>%
  mutate(retry_rate = ifelse(is.na(retry_rate), 0, retry_rate))
```

### **Number of retry each user & B status**

```{r}
number_user_retry_and_B_status <- number_user_retry %>%
  left_join(B_status_backend, by = "id") %>%
  mutate(B_num = ifelse(B_num>=1, 1, 0))
```

### **Number of retry each user & type user**

```{r}
number_user_retry_and_user_type <- number_user_retry %>%
  inner_join(user_type)
```

### **Number of retry each user & type user & B status**
```{r}
number_user_retry_and_B_status_and_user_type <- number_user_retry_and_B_status %>%
  inner_join(user_type)
```


## **Time different between 2 sequential events**

### **Time diff 15 minutes**

```{r}
time_diff <- front_end %>%
  arrange(date) %>%
  group_by(id) %>%
  mutate(next_date = lead(date),
         time_diff = as.numeric(difftime(
         strptime(next_date, format="%Y-%m-%d %H:%M:%S"),
         strptime(date, format="%Y-%m-%d %H:%M:%S"),
         units = "secs"))) %>%
  ungroup()

time_diff_count_900 <- time_diff %>%
  group_by(id) %>%
  filter(time_diff >= 900) %>%
  summarise(n = n()) 

time_diff_15_min <- time_diff %>%
  left_join(time_diff_count_900) %>%
  mutate(n = ifelse(is.na(n), 0, n)) %>%
  filter(time_diff <= 900) %>%
  ungroup() 
```

## **Front end fit date with back end**

```{r}
front_end_fit_date <- front_end_ui %>%
  filter(date >= min(back_end$date), date <= max(back_end$date))
```

# **Analysis**

## **Retry**

### **Biểu đồ cột cho số lần thử lại**

```{r}
number_user_retry %>%
  group_by(retry_rate) %>%
  summarise(n = n()) %>%
  arrange(desc(n)) %>%
  ggplot(aes(x = fct_reorder(as.factor(retry_rate), n), y = n)) +
  geom_col() +
  coord_flip() +
  labs(title = "Trên 42% những người sử dụng đã thử lại ít nhất 1 đến 4 lần",
       subtitle = "Hơn 50% lượng người sử dụng không thử lại",
       x = "Số lần thử lại",
       y = "Lượng người")

number_user_retry %>%
  group_by(retry_rate) %>%
  summarise(n = n()/3950) %>%
  arrange(desc(n))
```

### **Thử bỏ thêm filter người có status B**

```{r}
number_user_retry_and_B_status %>%
  group_by(retry_rate, B_num) %>%
  summarise(n = n()) %>%
  arrange(desc(n)) %>% 
  ggplot() +
  geom_col(aes(x = fct_reorder(as.factor(retry_rate), n), y = n, 
             fill = factor(B_num))) +
  coord_flip() +
  labs(title = "Những người có ít nhất 1 B result tập trung ở những người thử 0, 1, 2, 3, 4, 5 lần",
       subtitle = "",
       x = "Số lần thử lại",
       y = "Lượng người",
       fill = "Had B") 

number_user_retry_and_B_status %>%
  group_by(retry_rate, B_num) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  group_by(retry_rate) %>%
  mutate(n/sum(n))


number_user_retry_and_B_status_and_user_type %>%
  group_by(retry_rate, B_num, type) %>%
  summarise(n = n()) %>% 
  arrange(desc(n)) %>%
  ggplot() +
  geom_col(aes(x = fct_reorder(as.factor(retry_rate), -n), y = n, 
             fill = factor(B_num))) +
  facet_wrap(~ as.factor(type)) +
  labs(title = "",
       subtitle = "",
       x = "Số lần thử lại",
       y = "Lượng người",
       fill = "Had B") 
```

### **Thử bỏ thêm filter người sử dụng new hay old UI**

```{r}
number_user_retry_and_user_type %>%
  group_by(retry_rate, type) %>%
  summarise(n = n()) %>%
  arrange(desc(n)) %>%
  ggplot(aes(x = fct_reorder(as.factor(retry_rate), desc(n)), y = n, fill = type)) +
  geom_col() +
  geom_text(
    aes(label = n),
    colour = "black", size = 3,
    vjust = 1.5, position = position_dodge(.9)
  ) +
  labs(title = "Mối quan hệ e^(-x) có sự khác nhau giữa UI mới và cũ ",
       y = "Lượng người",
       x = "Số lần thử lại",
       fill = "Type of user")

number_user_retry_and_user_type %>%
  group_by(retry_rate, type) %>%
  summarise(n = n()) %>%
  arrange(desc(n)) %>%
  ggplot(aes(x = fct_reorder(as.factor(retry_rate), desc(n)), y = n, fill = type)) +
  geom_col() +
  geom_text(
    aes(label = n),
    colour = "black", size = 3,
    vjust = 1.5, position = position_dodge(.9)
  ) +
  geom_line(aes(factor(retry_rate), n, group = 1)) +
  geom_point(aes(factor(retry_rate), n)) +
  facet_wrap(~ type, scales = "free") +
  labs(title = "Mối quan hệ e^(-x) có sự khác nhau giữa UI mới và cũ ",
       y = "Lượng người",
       x = "Số lần thử lại",
       fill = "Type of user")
```

## **Front end**

### **xy8 là nút liên kết ngay**

```{r}
front_end_fit_date %>%
  inner_join(back_end_list_id, by = "id") %>%
  group_by(id) %>%
  arrange(date) %>%
  slice(n()-1,n()) %>%
  ungroup() %>%
  group_by(eventid) %>%
  summarise(n = n()) %>%
  arrange(desc(n))

front_end_fit_date %>%
  select(id) %>%
  unique() %>%
  inner_join(back_end, by = "id")
```

### **Interaction over hour using entire front end**

```{r}
front_end %>%
  mutate(hour = hour(date)) %>%
  group_by(hour) %>%
  summarise(n = n()) %>%
  ggplot(aes(x = factor(hour), y = n)) +
  geom_point() +
  geom_line(group = 1) +
  geom_hline(yintercept=8203, linetype="dashed", color = "blue", size = 1) +
  geom_hline(yintercept=7049, linetype="dashed", color = "red", size = 1) +
  geom_text(aes(0, 8203, label = "Mean-8203", vjust = -1, hjust = -1), size = 4) +
  geom_text(aes(0, 7049, label = "Median-7049", vjust = -1, hjust = -1), size = 4) 

front_end %>%
  mutate(hour = hour(date)) %>%
  group_by(hour) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  summarise(
            mean = mean(n),
            median = median(n))
```

### **Interaction over hour using fit front end**

```{r}
front_end_fit_date %>%
  mutate(hour = hour(date)) %>%
  group_by(hour) %>%
  summarise(n = n()) %>%
  ggplot(aes(x = factor(hour), y = n)) +
  geom_point() +
  geom_line(group = 1) +
  geom_hline(yintercept=4424, linetype="dashed", color = "blue", size = 1) +
  geom_hline(yintercept=4047, linetype="dashed", color = "red", size = 1) +
  geom_hline(yintercept=9014, linetype="dashed", color = "cyan", size = 1) +
  geom_hline(yintercept=1240, linetype="dashed", color = "black", size = 1) +
  geom_text(aes(0, 4424, label = "Mean-4424", vjust = -1, hjust = -1), size = 4) +
  geom_text(aes(0, 4047  , label = "Median-4047  ", vjust = -1, hjust = -1), size = 4) 

front_end_fit_date %>%
  mutate(hour = hour(date)) %>%
  group_by(hour) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  summarise(max = max(n),
            mean = mean(n),
            median = median(n),
            min = min(n))
```

## **Average time using of each user**

```{r}
time_using_each_id <- time_diff_15_min %>%
  group_by(id, screenid) %>%
  summarise(total_spend = sum(time_diff)/(n+1)) %>%
  unique()

time_using_each_id %>%
  inner_join(user_type) %>%
  inner_join(B_status_backend) %>%
  inner_join(number_user_retry) %>%
  ggplot(aes(x = total_spend, y = retry_rate)) +
  geom_point(aes(color = factor(type))) +
  facet_wrap(~ type) +
  geom_smooth(method = "lm", se = FALSE)

time_using_each_id %>%
  inner_join(user_type) %>%
  inner_join(B_status_backend) %>%
  inner_join(number_user_retry) %>%
  mutate(B_num = ifelse(B_num>=1, 1, 0)) %>%
  ggplot(aes(x = total_spend+1, y = retry_rate)) +
  geom_point(aes(color = factor(B_num))) +
  facet_wrap(~ type) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_log10()

avg_time <- time_using_each_id %>%
  inner_join(user_type) %>%
  inner_join(B_status_backend) %>%
  inner_join(number_user_retry) %>%
  mutate(B_num = ifelse(B_num>=1, 1, 0))

avg_time %>%
  ggplot(aes(x = type, y = total_spend)) +
  geom_boxplot()

avg_time %>%
  ggplot(aes(x = factor(B_num), y = total_spend)) +
  geom_boxplot()
```

```{r}
number_of_time_use_UI_of_user <- time_diff_15_min %>% 
  mutate(n = n+1) %>%
  select(id, n) %>%
  unique()

time_diff_15_min %>% 
  group_by(screenid) %>%
  summarise(sum = sum(time_diff)) %>%
  arrange(desc(sum))

back_end %>%
  inner_join(user_type) %>%
  group_by(id) %>%
  arrange(date) %>%
  slice(-1) %>%
  group_by(type, stepresult) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  gt::gt()
```

```{r}
avg_time_screenid<- time_diff_15_min %>%
  group_by(id, screenid) %>%
  summarise(total_spend = sum(time_diff)/(n+1)) %>%
  unique() %>%
  ungroup() %>%
  group_by(screenid) %>%
  summarise(avg = sum(total_spend)/n())

interaction_screen <- front_end_ui %>%
  group_by(screenid) %>%
  summarise(number_of_interaction = n())

eventid <- front_end_ui %>%
  select(eventid, screenid) %>%
  unique() %>%
  group_by(screenid) %>% 
  summarise(n = n()) %>%
  inner_join(avg_time_screenid, by = "screenid") %>%
  inner_join(interaction_screen, by = "screenid") %>%
  ungroup()

write.csv(eventid, "eventid.csv")

front_end_ui %>%
  unique() %>%
  filter(screenid != "11") %>%
  group_by(eventid) %>%
  summarise(n = n()) %>%
  arrange(desc(n))

front_end_ui %>%
  arrange(type, desc(id), date) %>% View()
```

```{r}
front_end %>%
  unique()

front_end 

time_diff <- time_diff %>% ungroup()
user_retry <- user_retry %>% ungroup()

time_diff %>%
  filter(!is.na(next_date)) 

time_using_each_id %>%
  ggplot(aes(x = total_spend+1, fill = factor(screenid))) +
  geom_histogram() +
  scale_x_log10() +
  facet_wrap(~ factor(screenid), scales = "free")

time_using_each_id %>%
  ggplot(aes(x = total_spend, fill = factor(screenid))) +
  geom_histogram() +
  facet_wrap(~ factor(screenid), scales = "free")

front_end %>%
  group_by(id, eventid) %>%
  unique() %>%
  summarise(n = n()) %>%
  arrange(desc(n))
  
front_end %>%
  filter(screenid != 11) %>%
  select(id, eventid) %>%
  unique() %>%
  group_by(id) %>%
  summarise(n = n()) %>% 
  ggplot(aes(x = n)) +
  geom_histogram(fill = "blue") +
  geom_vline(xintercept = 1, linetype="dashed", color = "red") +
  geom_vline(xintercept = 12, linetype="dashed", color = "red") 

front_end %>%
  filter(screenid != 11) %>%
  select(id, eventid) %>%
  unique() %>%
  group_by(id) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  summarize(
            P95 = quantile(n, 0.95),
            P5 = quantile(n, 0.05)) 

front_end %>%
  filter(id == "FFDBDJFJGCIJHBBACIA") %>% View()

arrange_front_end <- front_end_ui %>%
  arrange(id, date) 

write.csv(arrange_front_end, "arrange_front_end.csv")
```



